\vspace{-0.8cm}Vertex Coloring and Applications

### 2017-05-11 work/paper.tex
Adding labels to graphs

\begin{figure}[H]
  \includegraphics[width=\linewidth]{../poster/figures/plot-colors.pdf}
  \caption{Comparing number of colors used for the three heuristics}\label{fig:compare-colors}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\linewidth]{../poster/figures/plot-time.pdf}
  \caption{Comparing running time of each heuristic for each edge percentage}\label{fig:compare-time}
\end{figure}

>>>>

\begin{figure}[H]
  \includegraphics[width=\linewidth]{../poster/figures/plot-colors.pdf}
  \caption{Number of colors used for the three heuristics of graphs with 50, 100, 250, 500, \& 1000 vertices}\label{fig:compare-colors}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\linewidth]{../poster/figures/plot-time.pdf}
  \caption{Running time for each edge percentage of graphs with 50, 100, 250, 500, \& 1000 vertices}\label{fig:compare-time}
\end{figure}
